Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-05 notes.tex
oh god, what a blunder. Incorrectly calculated the general expression for the Greens function. Rectified the general part. Next need to do that for the specific case of the dimer

The local Hamiltonians look like
\begin{equation}\begin{aligned}
	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
\begin{equation}\begin{aligned}
	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N. of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
\begin{equation}\begin{aligned}
	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\). Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
\begin{equation}\begin{aligned}
	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
\end{aligned}\end{equation}
For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer. The Hubbard Hamiltonian can thus be obtained from the Anderson dimer using the following equation
\begin{equation}\begin{aligned}
	\label{H_tiled}
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
\section{Computing Greens functions and related quantities}
In terms of the Greens function, equation \ref{H_tiled} becomes
\begin{equation}\begin{aligned}
	\label{green_eq}
	\omega - {G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\left(\omega - {G_A}^{-1}(\omega)\right)\left(d, z \to i,j\right) + \left(\omega - {G_A}^{-1}(\omega)\right)\left(d,z \to j,i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
where $G_H$ and $G_A$ are the Hubbard and SIAM Greens functions:
\begin{equation}\begin{aligned}
	G_H(\omega) = \frac{1}{\omega - H_H}, && G_A(\omega) = \frac{1}{\omega - H_A}
\end{aligned}\end{equation}
Since the two $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor. Each will come with a factor which is just the total number of nearest neighbour pairs, which is $ \frac{Nw}{2}$. This allows them to cancel the $\omega$ on the LHS. The equation then simplifies to
\begin{equation}\begin{aligned}
	\label{green_eq_final}
	{G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\tilde G_A^{-1}(\omega, i, j) + \tilde G_A^{-1}(\omega, j, i)\right]
\end{aligned}\end{equation}
where $\tilde G_A^{-1}(\omega, i, j) = \omega - \tilde H^A(i, j)$, and $H^A(i, j)$ is defined as
\begin{equation}\begin{aligned}
	\tilde H^A(i, j) = -\frac{Nw}{2}t^H\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + N U^H\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
$\tilde H^A(i, j)$ is nothing but the Anderson molecule Hamiltonian, but with the impurity replaced by the $i^\text{th}$ site and the zero-mode replaced by the $j^\text{th}$ site. It is important to note that $\tilde G_A^{-1}(\omega, i, j)$ only scatters between the sites $i,j$.

We will now calculate the single-particle site diagonal and site offdiagonal Greens functions. First lets consider the diagonal Greens function at $i^\text{th}$ site. The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices. There will be $w$ such terms, because $i$ has $w$ nearest neighbours. Each such pair will have two terms, one with $i$ as the impurity and another with $i$ as the zero-mode. For the term that has $i$ as the impurity, the Greens function would then represent the impurity-diagonal Greens function $(G_{dd}^\sigma)$ of the zero-mode SIAM, while for the other term, the Greens function would represent the bath-diagonal or the zero-mode diagonal Greens function $(G_{zz}^\sigma)$.
\begin{equation}\begin{aligned}
	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]
\end{aligned}\end{equation}
Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$. This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$. The two terms for this nearest neighbour pair will be one for impurity as $i$ and the other for impurity as $j$. The Greens function will thus be the impurity-zero mode and zero mode-impurity Greens functions:
\begin{equation}\begin{aligned}
	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
\end{aligned}\end{equation}
Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space. Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$. For brevity, we therefore label them $g_0$ and $g_1$ respectively. 
\begin{equation}\begin{aligned}
	g_0 &\equiv \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]\\
	g_1 &\equiv \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
\end{aligned}\end{equation}

\begin{equation}\begin{aligned}
	G^{-1}_H(\omega) = \begin{pmatrix} \left(G^{-1}\right)_{00} & \left(G^{-1}\right)_{01} & ... & ... & \left(G^{-1}\right)_{0N}\\
		\left(G^{-1}\right)_{10} & \left(G^{-1}\right)_{11} & \left(G^{-1}\right)_{12} & ... & ...\\
		... & \left(G^{-1}\right)_{21} & \left(G^{-1}\right)_{22} & \left(G^{-1}\right)_{23} & ... \\
		    &&.&&\\
		    &&.&&\\
		    &&.&&\\
\end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
		g_1 & g_0 & g_1 & ... & ...\\
		... & g_1 & g_0 & g_1 & ... \\
		    &&...&&\\
		    &&...&&\\
\end{pmatrix} 
\end{aligned}\end{equation}
It can be written in the operator form as
\begin{equation}\begin{aligned}
	G_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)
\end{aligned}\end{equation}
We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
\begin{equation}\begin{aligned}
	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k}\\
	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\\
					&=\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
$\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice. $q_i$ are the projections of $\vec q$ along those vectors. $a_i$ are the lattice spacings along each primitive vector. Adding the Hermitian conjugate simply extracts the real part:
\begin{equation}\begin{aligned}
	\sum_i \ket{i}\bra{i} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}2\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
\end{aligned}\end{equation}
The inverse Greens function thus becomes diagonal in momentum space
\begin{equation}\begin{aligned}
G_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
	& g_0 + g_1\xi_{\vec k_2} && \\
	&& g_0 + g_1\xi_{\vec k_3} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
\begin{equation}\begin{aligned}
	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&& \\
	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} && \\
	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} & \\
	...&...&...&\\
	\end{pmatrix} 
\end{aligned}\end{equation}
The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.
\begin{equation}\begin{aligned}
	G_H(\vec k, \omega) &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
			    &= \left\{\frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}\right\}^{-1}
\end{aligned}\end{equation}

\section{Why this does not work}
Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:

@@

	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}

@@

For the Hubbard dimer, the set of momenta are $0, \frac{\pi}{a}$, so

@@

	\xi_{\vec k} = 2, -2

@@

Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as

@@

	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + 2g_1} + \frac{1}{g_0 - 2g_1}\right]  = \frac{g_0}{g_0^2 - 4g_1^2}

@@

$g_{0,1}$ are expressed in terms of the elements of the inverse Greens function matrix of the Anderson molecule. The inverse of a $2\times 2$ matrix is

@@

	G_A^{-1} = \frac{1}{\text{Det }G_A}\begin{pmatrix} \left(G_A\right)_{zz} &  -\left(G_A\right)_{zd} \\ -\left(G_A\right)_{zd} & \left(G_A\right)_{dd}\end{pmatrix} \implies \begin{cases}
		g_0 = \frac{1}{2} \frac{1}{\text{Det }G_A}\left[\left(G_A\right)_{zz} + \left(G_A\right)_{dd}\right] \\
		g_1 = -\frac{1}{\text{Det }G_A}\left(G_A\right)_{zd} \\
	\end{cases}

@@

The matrix elements of $G_A$ are calculated in the appendix. The actual real space local Greens function for the Hubbard dimer is also shown there. By comparing the Greens functions (for eg., eqs.~\ref{dimer_local_G} and \ref{mole_local_G}), one can see that the structures of the denominators are different. This is because of the fact that the eigenvalues for $n=1$ or $n=3$ of the Hubbard dimer are different from that for the Anderson molecule. This indicates that we need to change the auxiliary system (SIAM with non-interacting zero mode).

>>>>

The local Hamiltonians look like
\begin{equation}\begin{aligned}
	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
\begin{equation}\begin{aligned}
	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N. of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
\begin{equation}\begin{aligned}
	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\). Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
\begin{equation}\begin{aligned}
	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
\end{aligned}\end{equation}
For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer. The Hubbard Hamiltonian can thus be obtained from the Anderson molecule using the following equation:
\begin{equation}\begin{aligned}
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
The combination that is being summed over,
\begin{equation}\begin{aligned}
	H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)
\end{aligned}\end{equation}
is actually a Hubbard dimer Hamiltonian.
\begin{equation}\begin{aligned}
	&H^D(U^D, t^D) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)\\
	&H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = -2t^A\sum_\sigma\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + U^A\left( \tau_{i \uparrow}\tau_{i \downarrow} + \tau_{i \uparrow}\tau_{i \downarrow}\right)\\
	\implies &H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = H^D(0 \to i, 1 \to j, t^D \to 2t^A, U^D \to U^A)
\end{aligned}\end{equation}
The tiling can thus be actually done in terms of Hubbard dimers:
\begin{equation}\begin{aligned}
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to Nwt^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
For reasons that will become apparent later, we will scale the internal Hubbard dimer by half, pulling out a two:
\begin{equation}\begin{aligned}
	\label{H_tiled}
	H^H\left(t^H, U^H\right)  = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}
\end{aligned}\end{equation}

\section{Computing Greens functions and related quantities}
In terms of the Greens function, equation \ref{H_tiled} becomes

@@

	\label{green_eq}
	\omega - {G_H}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[\omega - G_D^{-1}\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}

@@

where $G_H$ and $G_A$ are the Greens functions for the full Hubbard and the Hubbard dimer respectively:

@@

	G_H(\omega) = \frac{1}{\omega - H^H}, && G_D(\omega) = \frac{1}{\omega - H^D}

@@

Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor. The factor is just the total number of nearest neighbour pairs, which is $\frac{Nw}{2}$. This allows it to cancel the $\omega$ on the LHS. The equation then simplifies to

@@

	\label{green_eq_final}
{G_H}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[G_D^{-1}\left(\omega, 1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}} = \frac{2}{Nw}\sum_{\left<i,j\right>}G_D^{-1}\left(\omega, i, j, t^D = \frac{1}{2}Nwt^H, U^D = \frac{1}{2}N U^H\right)

@@

where $G_D^{-1}(i,j,t^D,U^D)$ is the Greens function (matrix) of the Hubbard dimer Hamiltonian with $i, j$ as the two sites. Henceforth, we will supress the transformation rules in the arguments of the Greens function and assume they have been applied. For the record, the transformations are

@@

	t^D &= \frac{1}{2}Nwt^H\\
	U^D &= \frac{1}{2}N U^H

@@

\\\\
We will now calculate the single-particle site diagonal and site offdiagonal Greens functions. First lets consider the diagonal Greens function at $i^\text{th}$ site. The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices. There will be $w$ such terms, because $i$ has $w$ nearest neighbours. Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer. Each term will be a real space local Greens function, and because of translational invariance, it will be the same on both sites. So we will represent the real space local inverse Greens function as $\left[G_D^{-1}(\omega)\right]_{00\sigma}$. The entire thing is thus $w$ times this local Greens function.
	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{00\sigma}\times w = \frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} \equiv g_0
Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$. This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$. This will not be a diagonal Greens function. Instead, it involves two nearest neighbour sites. We call this Greens function $\left[G_D^{-1}(\omega)\right]_{01\sigma}$.
	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma} \equiv g_1
Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space. Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$. 
	G^{-1}_H(\omega) = \begin{pmatrix} \left(G^{-1}\right)_{00} & \left(G^{-1}\right)_{01} & ... & ... & \left(G^{-1}\right)_{0N}\\
		\left(G^{-1}\right)_{10} & \left(G^{-1}\right)_{11} & \left(G^{-1}\right)_{12} & ... & ...\\
		... & \left(G^{-1}\right)_{21} & \left(G^{-1}\right)_{22} & \left(G^{-1}\right)_{23} & ... \\
		    &&.&&\\
		    &&.&&\\
		    &&.&&\\
\end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
		g_1 & g_0 & g_1 & ... & ...\\
		... & g_1 & g_0 & g_1 & ... \\
		    &&...&&\\
		    &&...&&\\
\end{pmatrix} 
It can be written in the operator form as
	G_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)
We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k}\\
	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\\
					&=\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
$\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice. $q_i$ are the projections of $\vec q$ along those vectors. $a_i$ are the lattice spacings along each primitive vector. Adding the Hermitian conjugate simply extracts the real part:
	\sum_i \ket{i}\bra{i} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}2\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
The inverse Greens function thus becomes diagonal in momentum space
G_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
	& g_0 + g_1\xi_{\vec k_2} && \\
	&& g_0 + g_1\xi_{\vec k_3} & \\
	...&...&...&\\
	\end{pmatrix} 
The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&& \\
	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} && \\
	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} & \\
	...&...&...&\\
	\end{pmatrix} 
The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.
	G_H(\vec k, \omega) &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}
